Kidney disease \& Transplantations in Denmark

### 2017-04-20 LaTex/Paper.tex
Test
Jeg laver en test
teat
Cost effectiveness models section

@@

>>>>

\subsection{Cost Effectiveness Models }

When evaluating if a health program should be implemented or not, three different methods are commonly used; Cost Benefit Analysis (CBA), Cost Effectiveness Analysis (CEA) and Cost Utility Analysis (CUA). The approach and conclusion of the three methods differ, which makes them useful for different kinds of analyses. An effectiveness analysis consists of two parts, the costs and the effects of the intervention. The way the costs are estimated will generally be the same for the three effectiveness analyses, while the measurement of the effect will differ depending on the approach used (Christiansen; 2010). In the following we will outline the method for each of the effectiveness analysis above and from this deduct the method we will use in this paper.  
\\\\
The CBA is the simplest and least used effectiveness analysis of the three mentioned. A CBA will directly compare the monetary cost and benefit of one or more interventions and will always be conducted from the societies perspective. The CBA makes it easy to compare interventions because it is measured in monetary values, further more the CBA rests on the assumption that an intervention should only be implemented if the extra effectiveness (benefit) exceeds the extra cost of the intervention. (Edlin, McCabe, Hulme, Hall, Wright; 2014)
\\\\
A CEA relies on the assumption that the purpose of an effectiveness analysis should be to maximize what the decision maker would like to maximize. (Edlin, McCabe, Hulme, Hall, Wright; 2014) This means that a CEA only includes what the decision maker finds relevant, which additionally depends on the kind of decision maker, which could be society, public sector, health sector or something completely else. In contrast to a CBA, a CEA is measured in natural units such as Incremental Cost Utility Ratio, number of deaths avoided etc. It is worth to point out that the natural unit should be consistent, which means it cannot change depending on the individual or intervention looked at (Edlin, McCabe, Hulme, Hall, Wright; 2014). 
\\\\
CUA is seen as a sophisticated version of CEA. This is because CUA is utility based, which means the outcome of a CUA takes the patients health state into account opposed to a CEA. This is done by using quality adjusted life years (from now on referenced as QALY). This means that the effectiveness part of the analysis is weighted with how good the individual is feeling, 1 for perfect health, 0 for death. Due to this method we can compare how many QALY’s an intervention will produce compared to not implementing the intervention or implementing another intervention.

@@

\section{Intro 2}

Simons afsnit
